Ages of Planets and Stars Observed by Kepler

### 2024-04-20 paper/ms.tex
update ms

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{li_vs_teff_koi_X_S19S21dquality_eagles_logy.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Equivalent widths (EW) of the \ion{Li}{1} 6708\,\AA\ doublet
    from Keck/HIRES spectra collected between 2009 and 2024.}
    Lines are the ``mean'' isochrones from the same models as in Figure~\ref{fig:models}.
    The logarithmic scale highlights the dynamica range of both detections
    and upper limits.
%    The intrinsic
%    dispersion in the cluster data evolves in time, and is shown as
%    the $\pm$1$\sigma$ bands~\citep{Jeffries_2023}.
%    As for rotation-based ages, the intrisic dispersion sets the
%    empirical precision limit for the technique.
		\label{fig:li_vs_teff}
	}
\end{figure}

%TODO: does JUMP mirror all HIRES data from KOA?
We queried the internal CPS archive to collect all HIRES spectra that
were available for the \nplhoststarwgyroagewithgrazingandhighruwe\
stars for which rotation-based ages can be derived.
This exercise yielded at least one spectrum for \nlithiumstars\ and 
\nlithiumplanets\ planets.
We did not constrain whether the iodine cell was used, since
there are no relevant lines in the region of the 
\ion{Li}{1} 6708\,\AA\ doublet.
These observations were acquired between 6 September 2009 and 16
May 2024, primarily by the California Kepler Survey (CKS,
CITE).
In preparation for this study, we additionally collected {\bf XX}
spectra for ``confirmed'' planets with rotation-based ages below
1\,Gyr.

To measure the lithium equivalent widths, we followed the procedure
described by \citet{Bouma_2021}.
The stars of interest for this work are FGK stars, and so the
continuum in the vicinity of the
\ion{Li}{1} 6708\,\AA\ doublet is well-defined.
We therefore numerically integrate a single best-fit Gaussian over a
local window, and estimate the uncertainties on the line width through
a Monte Carlo procedure that bootstraps against the local scatter in the
continuum.
Generally speaking, this approach does not correct for the neighboring
\ion{Fe}{1} 6707.44\,\AA\ blend.

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{li_vs_teff_koi_X_S19S21dquality_eagles_logy.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Equivalent widths (EW) of the \ion{Li}{1} 6708\,\AA\ doublet
    from Keck/HIRES spectra collected between 2009 and 2024.} Lines
    are the ``mean'' isochrones from the same models as in
    Figure~\ref{fig:models}.  The logarithmic scale highlights the
    dynamica range of both detections and upper limits.
		\label{fig:li_vs_teff}
	}
\end{figure}

We queried the internal CPS archive to collect all blaze-corrected
HIRES spectra that were available for the
\nplhoststarwgyroagewithgrazingandhighruwe\ stars for which
rotation-based ages can be derived.  This query yielded at least one
spectrum for \nlithiumstars\ and \nlithiumplanets\ planets.  These
spectra were acquired between 6 September 2009 and 16 May 2024.  For
stars with multiple spectra available at varying ranges of
signal-to-noise (S/N), we analyzed only the spectrum with the highest
number of counts.

We measured the lithium equivalent widths following a procedure from
previous work \citep{Bouma_2021}.  The stars of interest for this work
are FGK stars, and so the continuum in the vicinity of the \ion{Li}{1}
6708\,\AA\ doublet is well-defined.  We therefore numerically
integrate a single best-fit Gaussian over a local window, and
estimated uncertainties on the line width through a Monte Carlo
procedure that bootstraps against the local scatter in the continuum.
This approach does not correct for the neighboring \ion{Fe}{1}
6707.44\,\AA\ blend.
